### 2018-11-20 paper.tex
Added live and non-live example figures
illustration of close event generated from close event

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:sweepA}
    \includegraphics[width=0.32\columnwidth]{fig1_a.png} }
  \subfloat[][]{
    \label{fig:sweepB}
    \includegraphics[width=0.32\columnwidth]{fig1_b.png} }
  \subfloat[][]{
    \label{fig:sweepC}
    \includegraphics[width=0.32\columnwidth]{fig1_c.png} } \\
  \subfloat[][]{
    \label{fig:sweepD}
    \includegraphics[width=0.32\columnwidth]{fig1_d.png} }
  \subfloat[][]{
    \label{fig:sweepE}
    \includegraphics[width=0.32\columnwidth]{fig1_e.png} }
  \subfloat[][]{
    \label{fig:sweepF}
    \includegraphics[width=0.32\columnwidth]{fig1_f.png} }
  \caption{Sweepline Algorithm
    \protect\subref{fig:sweepA} Here the algorithm has processed the first two events and multiple arc nodes have been added to the beach line, in which the leaf nodes represent active sites and the parent nodes are edge connections (as shown in \protect\subref{fig:sweepD}). It is important to note the beach line includes the edge connection 2-3 even though it is not shown here. The line created by this connection is the same as that made by 1-2.
    \protect\subref{fig:sweepB} Once the algorithm is able to triangulate a close event, it removes the arc node that formed it. This is illustrated in \protect\subref{fig:sweepE} where there is no longer an edge connection between 1-2 or 4-1.
    \protect\subref{fig:sweepC} When a site is enclosed completely by vertexes it is removed entirely from the beach line (as shown in \protect\subref{fig:sweepF}).
  }
  \label{fig:wavefront}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:sweepA}
    \includegraphics[width=0.32\columnwidth]{fig1_a.png} }
  \subfloat[][]{
    \label{fig:sweepB}
    \includegraphics[width=0.32\columnwidth]{fig1_b.png} }
  \subfloat[][]{
    \label{fig:sweepC}
    \includegraphics[width=0.32\columnwidth]{fig1_c.png} } \\
  \subfloat[][]{
    \label{fig:sweepD}
    \includegraphics[width=0.32\columnwidth]{fig1_d.png} }
  \subfloat[][]{
    \label{fig:sweepE}
    \includegraphics[width=0.32\columnwidth]{fig1_e.png} }
  \subfloat[][]{
    \label{fig:sweepF}
    \includegraphics[width=0.32\columnwidth]{fig1_f.png} }
  \caption{Sweepline Algorithm
    \protect\subref{fig:sweepA} Here the algorithm has processed the first two events and multiple arc nodes have been added to the beach line, in which the leaf nodes represent active sites and the parent nodes are edge connections (as shown in \protect\subref{fig:sweepD}). It is important to note the beach line includes the edge connection 2-3 even though it is not shown here. The line created by this connection is the same as that made by 1-2.
    \protect\subref{fig:sweepB} Once the algorithm is able to triangulate a close event, it removes the arc node that formed it. This is illustrated in \protect\subref{fig:sweepE} where there is no longer an edge connection between 1-2 or 4-1.
    \protect\subref{fig:sweepC} When a site is enclosed completely by vertexes it is removed entirely from the beach line (as shown in \protect\subref{fig:sweepF}).
  }
  \label{fig:sweepline}
\end{figure}

\begin{figure}
	\centering
	\subfloat[][]{
		\label{fig:live_event}
		\includegraphics[width=0.52\columnwidth]{fig2_a.png} }
	\subfloat[][]{
		\label{fig:live_event_tree}
		\includegraphics[width=0.52\columnwidth]{fig2_b.png} } \\
	\subfloat[][]{
		\label{fig:non_live}
		\includegraphics[width=0.52\columnwidth]{fig2_c.png} }
	\subfloat[][]{
		\label{fig:non_live_tree}
		\includegraphics[width=0.52\columnwidth]{fig2_d.png} }
	\caption{Illustration of live and non-live close events 
		\protect\subref{fig:live_event} Here lets examine nodes 16 and 11. It is known that a close event will occur where nodes 16, 11, and 10 arcs' will meet. Let's name this close event A.
		\protect\subref{fig:live_event_tree} Before we completely come to close on event A, node 22 gets added to the beach line and generates two new events. This causes  close event A to split into two new close events and therefore is considered a non-live close event. 
	}
	\label{fig:live_events}
\end{figure}

\begin{figure}
	\centering
	\subfloat[][]{
		\label{fig:close_eventA}
		\includegraphics[width=0.52\columnwidth]{fig3_a.png} }
	\subfloat[][]{
		\label{fig:close_eventB}
		\includegraphics[width=0.52\columnwidth]{fig3_b.png} } \\
	\subfloat[][]{
		\label{fig:close_eventC}
		\includegraphics[width=0.52\columnwidth]{fig3_c.png} }
	\subfloat[][]{
		\label{fig:close_eventD}
		\includegraphics[width=0.52\columnwidth]{fig3_d.png} }
	\caption{Illustration of close event generated from a close event
		\protect\subref{fig:close_eventA} Lets note the close event generated from node 10 closing with nodes 11 and 4. Lets name this close event B.
		\protect\subref{fig:close_eventB} Once event B is defined node 10 no longer creates an arc with node 11 and is removed. In this removal node 10's arc now maps to node 4's arc instead. As this happens a new close event is generated by arcs from nodes 11, 4 and 6.
	}
	\label{fig:close_events}
\end{figure}
